Incentivizing Exploration with Unbiased Histories

### 2019-01-30 COLT 2019 Submission/main.tex
COLT submission
update author name format

\documentclass[11pt]{article}
\usepackage{fullpage}
\usepackage{mathrsfs}
\usepackage{float}
% ======    PACKAGES
\usepackage{slivkins-setup,slivkins-theorems}
%\usepackage{amsmath, amsfonts, amssymb, amsthm, amsbsy, amscd, bm, bbm}
%\usepackage{amsbsy,amscd, bm, bbm}
\usepackage{kpfonts}
\usepackage{array}
\usepackage{booktabs}
\usepackage{graphicx}
\usepackage[small,bf]{caption}
\setlength{\captionmargin}{30pt}
\usepackage{subcaption}
\captionsetup[sub]{margin=10pt,font=small}
\usepackage{color}
\usepackage{ifthen}
\usepackage{xspace}
\usepackage[noend]{algorithmic}
\usepackage{algorithm}
\usepackage[colorlinks,citecolor={black},urlcolor={black},linkcolor={black}]{hyperref}
\usepackage{url}
\usepackage{tocbibind}
\usepackage{enumerate}
\usepackage{mdframed}
\usepackage{comment}
\usepackage{tikz}
\usetikzlibrary{decorations.pathreplacing}
\usepackage{cleveref}

\DeclareMathOperator*{\argmin}{argmin}

@@

%index on the tape
\def\z{\tau}
\title{Incentivizing Exploration with Unbiased Histories}

\author{
Nicole Immorlica \thanks{Microsoft Research, Cambridge, MA. Email: nicimm@microsoft.com.}
\and
Jieming Mao \thanks{University of Pennsylvania, Philadelphia, PA. email: maojm517@gmail.com. Results in this paper were obtained while J. Mao was an intern at Microsoft Research NYC.}
\and
Aleksandrs Slivkins  \thanks{Microsoft Research, New York, NY. email: slivkins@microsoft.com.}
\and
Zhiwei Steven Wu  \thanks{University of Minnesota, Minneapolis, MN. Email: zsw@umn.edu. Results in this paper were obtained while Z.S. Wu was a postdoc at Microsoft Research NYC.}
}
\begin{document}
\begin{titlepage}
\maketitle

@@

In this paper, we study a particular class of disclosure policies that use messages, called {\em unbiased subhistories}, consisting of the actions and rewards from by a subsequence of past agents, where the subsequence is chosen ahead of time. One trivial message of this form contains the full history; a disclosure policy that chooses to use such messages risks inducing herding behavior among the agents and thus has regret linear in the number of rounds.  Our main result is a disclosure policy using unbiased subhistories that obtains regret $\tilde{O}(\sqrt{T})$.  We also exhibit simpler policies with higher, but still sublinear, regret.  These policies can be interpreted as dividing a sublinear number of agents into constant-sized focus groups, whose histories are then fed to future agents.
\end{abstract}
\end{titlepage}

\input{intro}
\input{model}

@@

\bibliographystyle{plain}
\bibliography{bib-abbrv,bib-AGT,bib-bandits,bib-ML,bib-random,bib-slivkins}

\section*{Acknowledgment}
We would like to thank Robert Kleinberg for discussions in the early stage of this project.

\appendix
\input{prelim}
\input{app-warmup}
\input{3levelproofs}
\input{llevel}

>>>>

\documentclass[anon,12pt]{colt2019}
\usepackage{fullpage}
\usepackage{mathrsfs}
\usepackage{float}
% ======    PACKAGES
\usepackage{slivkins-setup}
%,slivkins-theorems}
%\usepackage{amsmath, amsfonts, amssymb, amsthm, amsbsy, amscd, bm, bbm}
%\usepackage{amsbsy,amscd, bm, bbm}
\usepackage{kpfonts}
\usepackage{array}
%\usepackage{booktabs}
\usepackage{graphicx}
%\usepackage[small,bf]{caption}
%\setlength{\captionmargin}{30pt}
%\usepackage{subcaption}
%\captionsetup[sub]{margin=10pt,font=small}
\usepackage{color}
\usepackage{ifthen}
\usepackage{xspace}
\usepackage[noend]{algorithmic}
\usepackage{algorithm}
%\usepackage[colorlinks,citecolor={black},urlcolor={black},linkcolor={black}]{hyperref}
\usepackage{url}
%\usepackage{tocbibind}
\usepackage{enumerate}
\usepackage{mdframed}
\usepackage{comment}
\usepackage{tikz}
\usetikzlibrary{decorations.pathreplacing}
\usepackage{cleveref}

\newtheorem{assumption}[theorem]{Assumption}
\newtheorem{construction}[theorem]{Construction}
\newtheorem{claim}[theorem]{Claim}
\DeclareMathOperator*{\argmin}{argmin}

@@

%index on the tape
\def\z{\tau}
\title{Incentivizing Exploration with Unbiased Histories}
\usepackage{times}

% Authors with different addresses:
\coltauthor{
\Name{Nicole Immorlica} \Email{nicimm@microsoft.com}\\
\addr Microsoft Research, Cambridge, MA. 
\and
\Name{Jieming Mao} \Email{maojm517@gmail.com}\\
\addr University of Pennsylvania, Philadelphia, PA.
\and
\Name{Aleksandrs Slivkins}  \Email{slivkins@microsoft.com}\\
\addr Microsoft Research, New York, NY.
\and
\Name{Zhiwei Steven Wu} \Email{zsw@umn.edu}\\
\addr University of Minnesota, Minneapolis, MN.
}
\begin{document}
\begin{titlepage}
\maketitle

@@

In this paper, we study a particular class of disclosure policies that use messages, called {\em unbiased subhistories}, consisting of the actions and rewards from by a subsequence of past agents, where the subsequence is chosen ahead of time. One trivial message of this form contains the full history; a disclosure policy that chooses to use such messages risks inducing herding behavior among the agents and thus has regret linear in the number of rounds.  Our main result is a disclosure policy using unbiased subhistories that obtains regret $\tilde{O}(\sqrt{T})$.  We also exhibit simpler policies with higher, but still sublinear, regret.  These policies can be interpreted as dividing a sublinear number of agents into constant-sized focus groups, whose histories are then fed to future agents.
\end{abstract}
\begin{keywords}%
  incentivizing exploration, multi-armed bandit, social learning
\end{keywords}
\end{titlepage}
\input{intro}
\input{model}

@@

%\bibliographystyle{plain}
%

%\acks{We would like to thank Robert Kleinberg for discussions in the early stage of this project.}
\bibliography{bib-abbrv,bib-AGT,bib-bandits,bib-ML,bib-random,bib-slivkins}
\appendix
\input{prelim}
\input{app-warmup}
\input{3levelproofs}
\input{llevel}
